---
title: "Mini-Project 2"
author: "Your Name Here"
date: "March 24, 2017"
output: html_document
---


## Loading the data


```{r, include=FALSE}
# load needed library and data 
library(tidyverse)
library(ggthemes)
library(maps)
library(ggplot2)

load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```


```{r}
#Creating file with total contributions for each state
money_from_state <- contributions%>%
  group_by(state)%>%
  summarise(total_amt=sum(transaction_amt))%>%
  arrange(desc(total_amt))
```

```{r}
#Creating file with total number of committees for each state
com_from_state <- committees%>%
  group_by(cmte_state)%>%
  summarise(total_com=n())%>%
  arrange(desc(total_com))%>%
  rename(state=cmte_state)

```

```{r}
#Creating file with total number of candidates from each state
cand_from_state <- candidates%>%
  group_by(cand_state)%>%
  summarise(total_cand=n())%>%
  arrange(desc(total_cand))%>%
  rename(state=cand_state)
```

```{r}
#Joining the three files together by state to create the file we're going to work with
joined_state <- money_from_state%>%
  inner_join(com_from_state,by="state")

joined_state <- joined_state%>%
  inner_join(cand_from_state,by="state")
```


```{r}
#Creating dot plot
ggplot(data=joined_state, aes(x=total_cand, y=total_com)) + geom_point(aes(col=total_amt, size=total_amt)) + guides(color=guide_legend(), size=guide_legend()) + scale_colour_gradient(low="light green", high="dark green")
```

# One Sentence Summary:
This graph shows the relationship among number of candidates, number of committe, and amount of contribution in each states. and we can find two "outlier" states: Virginia and DC, which have relatively small number of candidates but large number of committees and amount of contribution. 

# Background Information and Analysis 

The x-axis is the total number of candidates for each state, and the y-axis is the total number of committees for each state. The size and color of dots, which represent states, are mapped to the total amount of contribution from each state. 

Two biggest outlier states are DC and Virginia, which have relatively small number of candidates but large number of committees and amount of contribution. DC is capital of USA, so as a kind of political center, it should be more active in political campaign than other states. 